Supplement for: Carbon cycling in mature and regrowth forests globally

### 2021-02-24 manuscript/ERL_global_C_SI.Rmd
knit in new age trend figures
#69

#Age diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/manuscript/tables_figures/age_trends/", full.names = TRUE))) # first remove old files

@@

  knitr::include_graphics("tables_figures/age_trends/NEP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/GPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/NPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_woody.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_stem.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_foliage.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_litterfall.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_coarse.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_fine.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_eco.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_root.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_soil.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_het_soil.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_ag.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_ag_woody.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_foliage.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_coarse.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_fine.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_standing.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_down.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/organic_layer.png")
```

>>>>

#Age diagrams - for these, need to rename organic.layer and woody.mortality, replacing period with underscore.
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/manuscript/tables_figures/age_trends/", full.names = TRUE))) # first remove old files

@@

  knitr::include_graphics("tables_figures/age_trends/NEP_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/GPP_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/NPP_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_woody_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_stem_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_foliage_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_litterfall_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_coarse_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_fine_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_eco_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_root_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_soil_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_het_soil_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_ag_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_ag_woody_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_foliage_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_coarse_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_fine_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_standing_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_down_with_map.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/organic_layer_with_map.png")
```
